---
title: "Final Exam"
author: "21400022 YounhongKo"
date: '2020 6 16 '
output: html_document
---

## Read File
```{r}
load('final_test.RData')
```

## Import Library
```{r}
library(tidyr)
library(stringr)
library(ROCR)
```

## Declare Functions
```{r}
calAUC <- function(predCol, targetCol){
  perf <- performance(prediction(predCol, targetCol), 'auc')
  as.numeric(perf@y.values)
}
calcRMSE <- function(label, estimation){
  return(sqrt(mean((label - estimation) ** 2)))
}
calcR2 <- function(label, estimation){
  RSS = sum((label - estimation) ** 2)
  SStot = sum((label - mean(label)) ** 2)
  return(1-RSS/SStot)
}
```

# Part 1
## 1
```{r}
fmla <- "Revenue~."
shopping_model <- glm(fmla, data = shopping_train, family = binomial(link='logit'))
shopping_model
summary(shopping_model)
coefficients(shopping_model)
shopping_train$pred <- predict(shopping_model, newdata = shopping_train, type="response")
shopping_test$pred <- predict(shopping_model, newdata = shopping_test, type="response")

threshold <- 0.5
conf.shopping.train <- 
  table(pred=shopping_train$pred>threshold, actual=shopping_train$Revenue)
shopping_train_prec <- conf.shopping.train[2,2]/sum(conf.shopping.train[2,])
shopping_train_rec <- conf.shopping.train[2,2]/sum(conf.shopping.train[,2])
shopping_train_acc <- (conf.shopping.train[1,1] / (conf.shopping.train[1,1] + conf.shopping.train[1,2])
                       + conf.shopping.train[2,2] / (conf.shopping.train[2,1] + conf.shopping.train[2,2])) / 2
shopping_train_prec
shopping_train_rec
shopping_train_acc
calAUC(shopping_train$pred, shopping_train$Revenue)
```
>> With original given data field, calculate precision, recall, accuracy and AUC.

>> Precision: 0.752, Recall: 0.395, Accuracy: 0.825, AUC: 0.901

```{r}
fmla <- "Revenue~.+I(ExitRates^2)+I(PageValues^2)"
shopping_model <- glm(fmla, data = shopping_train, family = binomial(link='logit'))
shopping_train$pred <- predict(shopping_model, newdata = shopping_train, type="response")
shopping_test$pred <- predict(shopping_model, newdata = shopping_test, type="response")

threshold <- 0.2
conf.shopping.train <- 
  table(pred=shopping_train$pred>threshold, actual=shopping_train$Revenue)
shopping_train_prec <- conf.shopping.train[2,2]/sum(conf.shopping.train[2,])
shopping_train_rec <- conf.shopping.train[2,2]/sum(conf.shopping.train[,2])
shopping_train_acc <- (conf.shopping.train[1,1] / (conf.shopping.train[1,1] + conf.shopping.train[1,2])
                       + conf.shopping.train[2,2] / (conf.shopping.train[2,1] + conf.shopping.train[2,2])) / 2

calAUC(shopping_train$pred, shopping_train$Revenue)

prob_shopping_test <- shopping_test$pred
pred_shopping_test <- shopping_test$pred > threshold
```
>> Add more variables for models and set threshold to 0.2, test on website, and it surely increases accuracy and AUC.

>> Accuracy for test data: 0.826, AUC for test data: 0.896

# Part 2
## 1
```{r}
housing_train$X1 <- as.numeric(housing_train$X1)
housing_train$X1 <- as.character(housing_train$X1)
housing_train <- separate(housing_train, X1, c("Year", "Month"))
housing_train$Month <- ifelse(is.na(housing_train$Month), 0, housing_train$Month)
housing_train$Month <- str_pad(housing_train$Month, width=3, side="right", pad="0")
housing_train$Month <- as.numeric(housing_train$Month)
housing_train$Year <- as.numeric(housing_train$Year)

housing_test$X1 <- as.numeric(housing_test$X1)
housing_test$X1 <- as.character(housing_test$X1)
housing_test <- separate(housing_test, X1, c("Year", "Month"))
housing_test$Month <- ifelse(is.na(housing_test$Month), 0, housing_test$Month)
housing_test$Month <- str_pad(housing_test$Month, width=3, side="right", pad="0")
housing_test$Month <- as.numeric(housing_test$Month)
housing_test$Year <- as.numeric(housing_test$Year)
```
>> Data preparation step. Separate X1 into year and month, then save it as numeric variable.

```{r}
housing_model <- lm(Y ~ ., housing_train)
housing_model
summary(housing_model)
coefficients(housing_model)

housing_train$pred <- predict(housing_model, newdata = housing_train)
housing_test$pred <- predict(housing_model, newdata = housing_test)

calcRMSE(housing_train$Y, housing_train$pred)
calcR2(housing_train$Y, housing_train$pred)
```
>> Check RMSE and R2 with given data field.

>> RMSE: 8.19, R2: 0.60

```{r}
housing_model <- lm(Y ~ .+I(Month^2)+I(X2^2)+I(X3^2)+I(X4^2)+I(X5^2)
                    +I(Year^2)+I(Month^2)+I(X6^2)
                    +Month:X2+Month:X3+Month:X6
                    +X2:X3+X2:X4+X2:X5+X2:X6
                    +Year:Month+Year:X2+Year:X3+Year:X4+Year:X6
                    +X3:X4+X3:X5+X3:X6
                    +X4:X5+X4:X6, housing_train)
housing_train$pred <- predict(housing_model, newdata = housing_train)
housing_test$pred <- predict(housing_model, newdata = housing_test)

calcRMSE(housing_train$Y, housing_train$pred)
calcR2(housing_train$Y, housing_train$pred)
```
>> Try adding more variables and it is obvious that RMSE gets lower and R2 becomes higher.

>> RMSE for test data: 9.899, R2 for test data: 0.562

```{r}
pred_housing_test <- housing_test$pred
save(pred_housing_test, prob_shopping_test, pred_shopping_test, file="st21400022.RData")
```
>> Save the result to rdata file.